EldersAIR Health History Summary

### 2020-06-09 demographics_summary.Rmd
update file paths

```{r}
# Load individual datasets

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
elders_pm <- read_rds("Output/elders_pm_clean.rds")
```

>>>>

```{r}
# Load individual datasets
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds"))
```

### 2020-06-09 dustrak_data_cleaning.Rmd
update file paths

# Load, format, and save Dustrak log files
```{r}
## Box location: Update Box location once final data loaded
np_dustrak_initial <- read_xlsx("Input/NP/np_dustrak_20200220.xlsx") %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         dtid = as.factor(DTID),
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(DTLength),
         sample_ave = as.numeric(DTAverage),
         sample_min = as.numeric(DTMin),
         sample_max = as.numeric(DTMax),
         pm_comments = as.character(Comments),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)
#write_rds(np_dustrak_initial, "Output/np_dustrak.rds")

## Box location: Update Box location once final data loaded
nn_dustrak_initial <- read_xlsx("Input/NN/nn_dustrak_20200220.xlsx") %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         dtid = as.factor(DTID),
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(DTLength),
         sample_ave = as.numeric(DTAverage),
         sample_min = as.numeric(DTMin),
         sample_max = as.numeric(DTMax),
         pm_comments = "NA",
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)
#write_rds(nn_dustrak_initial, "Output/nn_dustrak.rds")

elders_dustrak_log <- rbind(np_dustrak_initial, nn_dustrak_initial)
#write_rds(elders_dustrak_log, "Output/elders_dustrak_log.rds")

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds") %>% 
  filter(winter_id == 1 | winter_id == 2)

elders_dustrak_log_new <- elders_dustrak_log %>% 
  left_join(elders_ids_linked, by = c("area", "home_winter_id")) %>% 
  arrange(home, winter_id)
#write_rds(elders_dustrak_log_new, "Output/elders_dustrak_log.rds")
```

@@

### NN ###
# List files
list_text_files <- list.files("Input/NN/nn_dustrak/pre_20200218/text")

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/NN/nn_dustrak/pre_20200218/text") # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = " ", skip = 28)) %>%
  unnest(save_data)

@@

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/NN/nn_dustrak/pre_20200218/text") # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = ",", skip = 28)) %>%
  unnest(save_data)

@@

### NP ###
# List files
list_text_files <- list.files("Input/NP/np_dustrak/pre_20200218/text")

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/NP/np_dustrak/pre_20200218/text") # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = ",", skip = 29,
                            col_names = c("date", "time", "pm"))) %>%
  unnest(save_data)

@@

### NN ###
# List files
list_csv_files <- list.files("Input/NN/nn_dustrak/pre_20200218/csv")

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/NN/nn_dustrak/pre_20200218/csv") # set new working directory
initial_data = tibble(file_name = list_csv_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

@@

### NP ###
# List files
list_csv_files <- list.files("Input/NP/np_dustrak/pre_20200218/csv")

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/NP/np_dustrak/pre_20200218/csv") # set new working directory
initial_data = tibble(file_name = list_csv_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

@@

##### Bind files from above #####
elders_pm <- rbind(nn_pm_csv, nn_pm_text_comma, nn_pm_text_space,
                   np_pm_csv, np_pm_text_comma) %>% 
  arrange(area, home, datetime_pm) %>% 
  ungroup()
# Save pm dataset as RDS 
# write_rds(elders_pm, "Output/elders_pm_full_raw.rds")
```

# Initial cleaning steps
## Remember to add correction factor
```{r}
elders_pm_full_raw <- read_rds("Output/elders_pm_full_raw.rds")
elders_dustrak_log <- read_rds("Output/elders_dustrak_log.rds") %>% 
  filter(winter_id == 1) %>% 
  arrange(home, sampling_visit) %>% 
  group_by(home, sampling_visit) %>% 
  distinct(home, .keep_all = TRUE)

@@

elders_pm_new2 <- elders_pm_new %>%   
  group_by(area, home, sampling_visit) %>% 
  # new variables summarizing pm2.5 within each home
  mutate(pm_total_observations = n(),
         # new datetime values to calculate sampling interval
         first_datetime = first(datetime_pm),
         last_datetime = last(datetime_pm),
         first_datetime = ymd_hms(first_datetime),
         last_datetime = ymd_hms(last_datetime),
         diff_datetime = interval(first_datetime, last_datetime),
         # total sampling interval, based on first and last datetimes
         pm_sample_interval = diff_datetime/86400,
         # expected number of observations with the sampling interval
         expected_obs = pm_sample_interval*24*60,
         # difference between actual and expected observations
         actual_vs_expected_diff = pm_total_observations - expected_obs,
         # indicator variable if actual vs expected obs > 10 or greater
         actual_vs_expected = if_else(actual_vs_expected_diff < 10 &
                                      actual_vs_expected_diff > -10, 1, 0),
         pm_mean = mean(pm),
         # breaking sampling period into days
         obs = row_number(),
         sampling_day = if_else(obs < 1441, 1, 0),
         sampling_day = if_else(obs < 2881 & obs > 1440, 2, sampling_day),
         sampling_day = if_else(obs < 4321 & obs > 2880, 3, sampling_day)) %>%
  # calculate pm means for each sampling day
  group_by(area, home, sampling_day) %>% 
  mutate(pm_mean_daily = mean(pm),
         pm_sampling_day = sampling_day) %>%
  unite(start_datetime_pm, c("start_date_pm", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(start_datetime_pm = ymd_hms(start_datetime_pm),
         pm_start_diff = interval(first_datetime, start_datetime_pm),
         pm_start_diff_hrs = pm_start_diff/3600) %>% 
  ungroup() %>% 
  select(-obs, -sampling_day) %>% 
  arrange(area, home, sampling_visit) 
# write_rds(elders_pm_new2, "Output/elders_pm_new.rds")

pm_summary <- elders_pm_new2 %>% 
  group_by(area, home, sampling_visit) %>%
  distinct(sampling_visit, .keep_all = TRUE)
# write_csv(pm_summary, "Output/elders_pm_summary.csv")
```

# Check sample start times and PM values
```{r}
# Load data 
elders_pm <- read_rds("Output/elders_pm_new.rds")

# Checking difference between dustrak start datetime and field data log datetime
sample_times <- elders_pm %>% 
  group_by(area, home, home_winter_id, sampling_visit) %>% 
  arrange(datetime_pm) %>% 
  mutate(pm_sd = sd(pm, na.rm = TRUE),
         pm_min = min(pm, na.rm = TRUE),
         pm_med = median(pm, na.rm = TRUE),
         pm_max = max(pm, na.rm = TRUE),
         starttime_diff = (datetime_pm - start_datetime_pm)/60) %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, datetime_pm, first_datetime,
         start_datetime_pm, last_datetime, pm_total_observations, pm_sample_interval,
         expected_obs, actual_vs_expected_diff, pm_mean, pm_sd, pm_min, pm_med, pm_max,
         starttime_diff) %>% 
  distinct(sampling_visit, .keep_all = TRUE) %>% 
  arrange(area, home, home_winter_id, sampling_visit)
# write_csv(sample_times, "Output/pm_sample_times_comparison.csv")
```

# Histogram for distribution of PM by individual ID
```{r}
# Load data 
elders_pm <- read_rds("Output/elders_pm_clean.rds")

@@

# Run function from above to look at results
## Function run for each household to check for odd trends/gaps in the data
## Notes from this process on uploaded to Box:
### EldersAIR > Ethan - data cleaning and analysis > pm_cleaning_summary
```{r}
# Load data 
elders_pm <- read_rds("Output/elders_pm_clean.rds")

@@

# Fix PM data after checking odd values and time differences
```{r}
# Load data 
elders_pm <- read_rds("Output/elders_pm_new.rds")

pm_sample_times_comparison <- read_xlsx("Input/pm_sample_times_comparison.xlsx") %>% 
  select(area, home, winter_id, sampling_visit, cleaning_comments, 
         next_steps, sensitivity_analysis) %>% 
  mutate(winter_id = as.factor(winter_id),
         sampling_visit = as.factor(sampling_visit))

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds") %>% 
  filter(winter_id == 1) %>% 
  select(area, home, winter_id, home_winter_id, home_id, treatment) %>% 
  distinct(home, .keep_all = TRUE)

@@

#write_rds(elders_pm_new, "Output/elders_pm_clean.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load, format, and save Dustrak log files
```{r}
## Box location: Update Box location once final data loaded
np_dustrak_initial <- read_xlsx(paste0(file_path, "Input/NP/np_dustrak_20200220.xlsx")) %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         dtid = as.factor(DTID),
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(DTLength),
         sample_ave = as.numeric(DTAverage),
         sample_min = as.numeric(DTMin),
         sample_max = as.numeric(DTMax),
         pm_comments = as.character(Comments),
         sampling_visit = as.factor(SamplingVisit),
         area = "NP") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)
#write_rds(np_dustrak_initial, paste0(file_path, "Output/np_dustrak.rds"))

## Box location: Update Box location once final data loaded
nn_dustrak_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_dustrak_20200220.xlsx")) %>% 
  # rename variables
  separate(StartTime, c("trash1", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  separate(StopTime, c("trash1", "stop_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(home_winter_id = as.factor(HomeWinterID),
         dtid = as.factor(DTID),
         start_date_pm = ymd(StartDate),
         start_time_pm = as.character(start_time_pm),
         stop_date_pm = ymd(StopDate),
         stop_time_pm = as.character(stop_time_pm),
         sample_obs = as.numeric(DTLength),
         sample_ave = as.numeric(DTAverage),
         sample_min = as.numeric(DTMin),
         sample_max = as.numeric(DTMax),
         pm_comments = "NA",
         sampling_visit = as.factor(SamplingVisit),
         area = "NN") %>% 
  select(home_winter_id, area, dtid, sampling_visit, start_date_pm, start_time_pm,
         stop_date_pm, stop_time_pm, sample_obs, sample_ave, sample_min,
         sample_max, pm_comments) %>% 
  arrange(home_winter_id)
#write_rds(nn_dustrak_initial, paste0(file_path, "Output/nn_dustrak.rds"))

elders_dustrak_log <- rbind(np_dustrak_initial, nn_dustrak_initial)
#write_rds(elders_dustrak_log, paste0(file_path, "Output/elders_dustrak_log.rds"))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds")) %>% 
  filter(winter_id == 1 | winter_id == 2)

elders_dustrak_log_new <- elders_dustrak_log %>% 
  left_join(elders_ids_linked, by = c("area", "home_winter_id")) %>% 
  arrange(home, winter_id)
#write_rds(elders_dustrak_log_new, paste0(file_path, "Output/elders_dustrak_log.rds"))
```

@@

### NN ###
# List files
list_text_files <- list.files(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/text"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = " ", skip = 28)) %>%
  unnest(save_data)

@@

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = ",", skip = 28)) %>%
  unnest(save_data)

@@

### NP ###
# List files
list_text_files <- list.files(paste0(file_path, "Input/NP/np_dustrak/pre_20200218/text"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NP/np_dustrak/pre_20200218/text")) # set new working directory
initial_data = tibble(file_name = list_text_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_delim, delim = ",", skip = 29,
                            col_names = c("date", "time", "pm"))) %>%
  unnest(save_data)

@@

### NN ###
# List files
list_csv_files <- list.files(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/csv"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NN/nn_dustrak/pre_20200218/csv")) # set new working directory
initial_data = tibble(file_name = list_csv_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

@@

### NP ###
# List files
list_csv_files <- list.files(paste0(file_path, "Input/NP/np_dustrak/pre_20200218/csv"))

# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/NP/np_dustrak/pre_20200218/csv")) # set new working directory
initial_data = tibble(file_name = list_csv_files) %>% # use list of files from above
  mutate(save_data = lapply(file_name, read_csv)) %>%
  unnest(save_data)

@@

##### Bind files from above #####
elders_pm <- rbind(nn_pm_csv, nn_pm_text_comma, nn_pm_text_space,
                   np_pm_csv, np_pm_text_comma) %>% 
  arrange(area, home, datetime_pm) %>% 
  ungroup()
# Save pm dataset as RDS 
# write_rds(elders_pm, paste0(file_path, "Output/elders_pm_full_raw.rds"))
```

# Initial cleaning steps
## Remember to add correction factor
```{r}
elders_pm_full_raw <- read_rds(paste0(file_path, "Output/elders_pm_full_raw.rds"))
elders_dustrak_log <- read_rds(paste0(file_path, "Output/elders_dustrak_log.rds")) %>% 
  filter(winter_id == 1) %>% 
  arrange(home, sampling_visit) %>% 
  group_by(home, sampling_visit) %>% 
  distinct(home, .keep_all = TRUE)

@@

elders_pm_new2 <- elders_pm_new %>%   
  group_by(area, home, sampling_visit) %>% 
  # new variables summarizing pm2.5 within each home
  mutate(pm_total_observations = n(),
         # new datetime values to calculate sampling interval
         first_datetime = first(datetime_pm),
         last_datetime = last(datetime_pm),
         first_datetime = ymd_hms(first_datetime),
         last_datetime = ymd_hms(last_datetime),
         diff_datetime = interval(first_datetime, last_datetime),
         # total sampling interval, based on first and last datetimes
         pm_sample_interval = diff_datetime/86400,
         # expected number of observations with the sampling interval
         expected_obs = pm_sample_interval*24*60,
         # difference between actual and expected observations
         actual_vs_expected_diff = pm_total_observations - expected_obs,
         # indicator variable if actual vs expected obs > 10 or greater
         actual_vs_expected = if_else(actual_vs_expected_diff < 10 &
                                      actual_vs_expected_diff > -10, 1, 0),
         pm_mean = mean(pm),
         # breaking sampling period into days
         obs = row_number(),
         sampling_day = if_else(obs < 1441, 1, 0),
         sampling_day = if_else(obs < 2881 & obs > 1440, 2, sampling_day),
         sampling_day = if_else(obs < 4321 & obs > 2880, 3, sampling_day)) %>%
  # calculate pm means for each sampling day
  group_by(area, home, sampling_day) %>% 
  mutate(pm_mean_daily = mean(pm),
         pm_sampling_day = sampling_day) %>%
  unite(start_datetime_pm, c("start_date_pm", "start_time_pm"), sep = " ", remove = FALSE) %>% 
  mutate(start_datetime_pm = ymd_hms(start_datetime_pm),
         pm_start_diff = interval(first_datetime, start_datetime_pm),
         pm_start_diff_hrs = pm_start_diff/3600) %>% 
  ungroup() %>% 
  select(-obs, -sampling_day) %>% 
  arrange(area, home, sampling_visit) 
# write_rds(elders_pm_new2, paste0(file_path, "Output/elders_pm_new.rds"))

pm_summary <- elders_pm_new2 %>% 
  group_by(area, home, sampling_visit) %>%
  distinct(sampling_visit, .keep_all = TRUE)
# write_csv(pm_summary, paste0(file_path, "Output/elders_pm_summary.csv"))
```

# Check sample start times and PM values
```{r}
# Load data 
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_new.rds"))

# Checking difference between dustrak start datetime and field data log datetime
sample_times <- elders_pm %>% 
  group_by(area, home, home_winter_id, sampling_visit) %>% 
  arrange(datetime_pm) %>% 
  mutate(pm_sd = sd(pm, na.rm = TRUE),
         pm_min = min(pm, na.rm = TRUE),
         pm_med = median(pm, na.rm = TRUE),
         pm_max = max(pm, na.rm = TRUE),
         starttime_diff = (datetime_pm - start_datetime_pm)/60) %>% 
  select(area, home, home_winter_id, winter_id, sampling_visit, datetime_pm, first_datetime,
         start_datetime_pm, last_datetime, pm_total_observations, pm_sample_interval,
         expected_obs, actual_vs_expected_diff, pm_mean, pm_sd, pm_min, pm_med, pm_max,
         starttime_diff) %>% 
  distinct(sampling_visit, .keep_all = TRUE) %>% 
  arrange(area, home, home_winter_id, sampling_visit)
# write_csv(sample_times, paste0(file_path, "Output/pm_sample_times_comparison.csv"))
```

# Histogram for distribution of PM by individual ID
```{r}
# Load data 
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds"))

@@

# Run function from above to look at results
## Function run for each household to check for odd trends/gaps in the data
## Notes from this process on uploaded to Box:
### EldersAIR > Ethan - data cleaning and analysis > pm_cleaning_summary
```{r}
# Load data 
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_clean.rds"))

@@

# Fix PM data after checking odd values and time differences
```{r}
# Load data 
elders_pm <- read_rds(paste0(file_path, "Output/elders_pm_new.rds"))

pm_sample_times_comparison <- read_xlsx(paste0(file_path, "Input/pm_sample_times_comparison.xlsx")) %>% 
  select(area, home, winter_id, sampling_visit, cleaning_comments, 
         next_steps, sensitivity_analysis) %>% 
  mutate(winter_id = as.factor(winter_id),
         sampling_visit = as.factor(sampling_visit))

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds")) %>% 
  filter(winter_id == 1) %>% 
  select(area, home, winter_id, home_winter_id, home_id, treatment) %>% 
  distinct(home, .keep_all = TRUE)

@@

#write_rds(elders_pm_new, paste0(file_path, "Output/elders_pm_clean.rds"))
```

### 2020-06-09 elders_health_data_cleaning.Rmd
update file paths

```{r}
# Load data
elders_ids_linked <- read_rds("Output/elders_ids_linked.rds")
```

@@

# Load and merge files from different locations
```{r}
nn_athomelog_initial <- read_xlsx("Input/NN/nn_athome_20200225.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NN",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

np_athomelog_initial <- read_xlsx("Input/NP/np_athomelog_20200225.xlsx") %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NP",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

@@

write_csv(save_var_names, "Output/at_home_var_names.csv")
```

@@

# Load and merge files from different locations
```{r}
nn_healthhistory_initial <- read_xlsx("Input/NN/nn_healthhistory_20200225.xlsx") %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignorereason) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

np_healthhistory_initial <- read_xlsx("Input/NP/np_healthhistory_20200225.xlsx") %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NP",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignoremissingdata) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

@@

write_csv(save_var_names, "Output/health_hx_var_names.csv")
```

@@

# Load and merge files from different locations
```{r}
nn_healthextra_initial <- read_xlsx("Input/NN/nn_healthextra_20200225.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

np_healthextra_initial <- read_xlsx("Input/NP/np_healthextra_20200225.xlsx") %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NP",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

@@

write_csv(save_var_names, "Output/health_extra_var_names.csv")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")

# Load data
elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds"))
```

@@

# Load and merge files from different locations
```{r}
nn_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_athome_20200225.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NN",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

np_athomelog_initial <- read_xlsx(paste0(file_path, "Input/NP/np_athomelog_20200225.xlsx")) %>% 
  mutate(home_winter_id = as.character(HomeWinterID),
         adult_id_num = as.character(AdultID),
         area = "NP",
         sampling_visit = as.numeric(SamplingVisit),
         at_home_day = as.factor(Day),
         at_home_7 = as.factor(AtHome1),
         at_home_8 = as.factor(AtHome2),
         at_home_9 = as.factor(AtHome3),
         at_home_10 = as.factor(AtHome4),
         at_home_11 = as.factor(AtHome5),
         at_home_12 = as.factor(AtHome6),
         at_home_13 = as.factor(AtHome7),
         at_home_14 = as.factor(AtHome8),
         at_home_15 = as.factor(AtHome9),
         at_home_16 = as.factor(AtHome10),
         at_home_17 = as.factor(AtHome11),
         at_home_18 = as.factor(AtHome12),
         at_home_19 = as.factor(AtHome13),
         at_home_20 = as.factor(AtHome14),
         at_home_21 = as.factor(AtHome15),
         at_home_22 = as.factor(AtHome16)) %>% 
  select(home_winter_id:at_home_22)

@@

write_csv(save_var_names, paste0(file_path, "Output/at_home_var_names.csv"))
```

@@

# Load and merge files from different locations
```{r}
nn_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_healthhistory_20200225.xlsx")) %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignorereason) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

np_healthhistory_initial <- read_xlsx(paste0(file_path, "Input/NP/np_healthhistory_20200225.xlsx")) %>% 
  rename_all(~str_replace_all(., "Date", "_date")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NP",
         rheum_arth = ra,
         rheum_arth_date = ra_date) %>% 
  select(-id:-homewinterid, -ra, -ra_date, -whatmissing:-ignoremissingdata) %>% 
  select(home_winter_id, adult_id_num, area, rheum_arth, rheum_arth_date,
         lupus:cigarspipes)

@@

write_csv(save_var_names, paste0(file_path, "Output/health_hx_var_names.csv"))
```

@@

# Load and merge files from different locations
```{r}
nn_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NN/nn_healthextra_20200225.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NN",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

np_healthextra_initial <- read_xlsx(paste0(file_path, "Input/NP/np_healthextra_20200225.xlsx")) %>% 
  rename_all(tolower) %>% 
  mutate(home_winter_id = as.character(homewinterid),
         adult_id_num = as.character(adultid),
         area = "NP",
         sampling_visit = samplingvisit) %>% 
  select( home_winter_id, adult_id_num, sampling_visit, area, cold2m:bronch2mdr)

@@

write_csv(save_var_names, paste0(file_path, "Output/health_extra_var_names.csv"))
```

### 2020-06-09 fitbit_cleaning.Rmd
update file paths

# Load files
```{r}
list_excel_files <- list.files("Input/fitbit_navajo_excel")
# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/fitbit_navajo_excel")
initial_data <- tibble(file_name = list_excel_files) %>%
  mutate(save_data = lapply(file_name, read_excel, skip = 0)) %>%
  unnest(save_data)

list_csv_files <- list.files("Input/fitbit_navajo_csv")
# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd("Input/fitbit_navajo_csv")
initial_data <- tibble(file_name = list_csv_files) %>%
  mutate(save_data = lapply(file_name, read_csv, skip = 1)) %>%
  unnest(save_data) 
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

# Load files
```{r}
list_excel_files <- list.files(paste0(file_path, "Input/fitbit_navajo_excel"))
# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/fitbit_navajo_excel"))
initial_data <- tibble(file_name = list_excel_files) %>%
  mutate(save_data = lapply(file_name, read_excel, skip = 0)) %>%
  unnest(save_data)

list_csv_files <- list.files(paste0(file_path, "Input/fitbit_navajo_csv"))
# Set working directory and load files in list; extract file name and add as column
## run next 4 lines together
setwd(paste0(file_path, "Input/fitbit_navajo_csv"))
initial_data <- tibble(file_name = list_csv_files) %>%
  mutate(save_data = lapply(file_name, read_csv, skip = 1)) %>%
  unnest(save_data) 
```

### 2020-06-09 health_history_summary.Rmd
update file paths

@@

elders_ids_linked <- read_rds("Output/elders_ids_linked.rds") %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)

elders_at_home_log <- read_rds("Output/elders_at_home_log.rds")
elders_health_hx <- read_rds("Output/elders_health_hx.rds")
elders_health_extra <- read_rds("Output/elders_health_extra.rds")
```

>>>>

```{r}
file_path <- c("C:/Users/ethan.walker/Box/Ethan Walker UM/R/EldersAIR/")
```

@@

elders_ids_linked <- read_rds(paste0(file_path, "Output/elders_ids_linked.rds")) %>% 
  filter(winter_id == 1 | winter_id == 2) %>% 
  arrange(area, adult_id_num)

elders_at_home_log <- read_rds(paste0(file_path, "Output/elders_at_home_log.rds"))
elders_health_hx <- read_rds(paste0(file_path, "Output/elders_health_hx.rds"))
elders_health_extra <- read_rds(paste0(file_path, "Output/elders_health_extra.rds"))
```
